Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-03-27 automatica/paper.tex
Addressed comments in sec 3.3

In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}. [ADD REFERENCE(S).]

We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
where $P$ ranges over functions (where a function is represented by the program computing it),
$a$ ranges over ground terms, 
and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some finite [CHECK: finite? are we doing only SAT or also SMT?] domain~$\mathcal{D}$. 
This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms. 
CEGIS breaks down this generally hard synthesis problem into two easier parts.

The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
[COMMENT ON TERMINATION?]
CEGIS in general is not guaranteed to terminate if the search space is infinite. 
%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------

>>>>

In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, as illustrated in Figure~\ref{fig:CEGIS}.

We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
where $P$ ranges over functions (where a function is represented by the program computing it),
$a$ ranges over ground terms, 
and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some domain~$\mathcal{D}$. 
This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms.

CEGIS breaks down this generally hard synthesis problem into two easier parts:
%The design consists of two phases,
an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.
Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
If the solution space is finite then the CEGIS loop is guaranteed to
terminate by either finding a solution or showing that no solution
exists.
%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------
